The reads in the COI mapped samples mapped to hundreds of references. I am hoping that there is one references that took a majority of those reads, so there is a clear winner here.

```{r}
# BOILER PLATE
library(dplyr)
```

# REAL DATA -------------------------------------------

The COI dataset is from Bold System, after running rmdup, and selecting specifically for COI sequences representing species only (no higher order taxa represented).

```{r}
# load data from collected columns file 
data <- read.csv(file = "../../Data/pathoscope_coi_rmdup_COIonly_speciesOnly/CombinedTableAllSamples.txt", 
                 header = TRUE,
                 sep = "\t")

# Set number of top values to plot
top_x = as.integer(10)

# initiate for loop
for (i in colnames(data)){
  
  data_sample <- data.frame(data[,i], row.names = row.names(data)) %>% # Pull rows
    sort_by(y = data[,i], decreasing = TRUE) # sort values from largest to smallest
  
  # select top_x values
  data_sample <- data.frame(data_sample[1:top_x,], 
                            row.names = row.names(data_sample)[1:top_x])
  
  # print pie chart
  par(mar=c(5,15,5,15), cex = 0.75)
  pie(data_sample$data_sample.1.top_x..., 
      labels = row.names(data_sample), 
      main = i) # change chart name

}
```

The COIs in the reference used here is the same as above EXCEPT that we also used cdhit to remove redundancy (I also think it removed any reference with a "-" in it, which was a lot of them).

```{r}
# load data from collected columns file 
data <- read.csv(file = "../../Data/pathoscope_rmdup_COIonly_speciesOnly_cdhit/CombinedTableAllSamples.txt", 
                 header = TRUE,
                 sep = "\t")

# Set number of top values to plot
top_x = as.integer(10)

# initiate for loop
for (i in colnames(data)){
  
  data_sample <- data.frame(data[,i], row.names = row.names(data)) %>% # Pull rows
    sort_by(y = data[,i], decreasing = TRUE) # sort values from largest to smallest
  
  # select top_x values
  data_sample <- data.frame(data_sample[1:top_x,], 
                            row.names = row.names(data_sample)[1:top_x])
  
  # print pie chart
  par(mar=c(5,15,5,15), cex = 0.75)
  pie(data_sample$data_sample.1.top_x..., 
      labels = row.names(data_sample), 
      main = i) # change chart name

}
```

