---
title: "Process_abundance_table"
author: "Caitlin Loeffler"
date: "2025-06-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Boiler Plate

```{r}
library(dplyr)
library(ggplot2)
library(tibble)
library(readxl)
library(hilldiv)
library(vegan)
```

## Get the abundance data

```{r}
# The data fresh out of the pathoscope alignment oven
# data_start <- read.table('D://Users/Caitlin/Documents/Research/Crandall Lab/Transcriptomics/USDA_aphids/Data/CombinedTableAllSamples_Pathoscope_main.txt',
#                          header = TRUE,
#                          # row.names = "X",
#                          sep = '\t')

# data_small_thisOne <- read.table('D://Users/Caitlin/Documents/Research/Crandall Lab/Transcriptomics/USDA_aphids/Data/CombinedTableAllSamples_smallref_ThisOne.txt',
#                          header = TRUE,
#                          #row.names = "X",
#                          sep = '\t')

data_full <- read.delim("../../Data/CombinedTableAllSamples_full.tsv", 
                        header = TRUE, 
                        row.names = "X",
                        sep = "\t") %>%
  t() %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "X") %>% 
  mutate(X = sub("\\.sam\\.report$", "", X)) %>% # remove ".sam.report"
  mutate(X = sub("_S\\d+", "", X)) %>% 
  column_to_rownames(var = "X") %>% 
  t() %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "X") %>% 
  as.data.frame() 
  
# # Now the relative abundance table of that
# data_full_RelAbund <- data_full %>% 
#   column_to_rownames(var = "X") %>% 
#   tss(.) %>% 
#   rownames_to_column(var = "X") %>% 
#   as.data.frame(.)
```

## Grab the metadata table

```{r}
metadata <- read_excel(path = "../../Data/Owen_insect_tissues_WorkSheet.xlsx", 
                       sheet = "GWU_RNAseq_2024") %>%
  filter(!if_all(everything(), is.na)) %>% 
  select(Number, Family, `Collection Date`) 
```

## Get the mapper files

And correct the mapper_suppressed file that got a little mixed up on the HPC.

```{r}
# Get the two mapper files
mapper_reliable <- read.delim("../../Data/Accession_taxid_lineage.tsv", 
                     header = TRUE,
                     sep = "\t", 
                     fill = TRUE) %>% 
  distinct() %>% 
  column_to_rownames(var = "Accession")


mapper_suppressed <- read.delim("../../Data/Suppressed_accession_taxid_lineage_updated.tsv", 
                                header = TRUE,
                                sep = "\t", 
                                row.names = 1) %>% # Make the Accessions the row names
  select(TaxID, Domain, Kingdom, Phylum, Class, Order, Family, Genus, Species, Full_name, Rank)

mapper <- rbind(mapper_reliable, mapper_suppressed)

# # The mapper_suppressed has some columns out of order, we are going to reorder them
# unordered_columns <- mapper_suppressed %>% 
#   filter(Full_name == "") %>% 
#   select(TaxID, Status, Comment, Domain, Kingdom, Phylum, Class, Order, Family, Genus, 
#          Species, Full_name, Rank) # Reorder the columns
# #Rename the columns
# colnames(unordered_columns) <- c("TaxID", "Domain", "Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "Species", "Full_name", "Rank", "Status", "Comment")
# # Now remake the mapper_suppressed table
# mapper_suppressed <- mapper_suppressed %>% 
#   filter(Full_name != "") %>% # Isolate the lines that are fine
#   rbind(., unordered_columns) # Bind the rows with corrected order of columns
# rm(unordered_columns)
# # Save the new table
# write.table(mapper_suppressed, file = "../../Data/Suppressed_accession_taxid_lineage_updated.tsv",
#             quote = FALSE, row.names = TRUE, sep = "\t")
```

Check that all the refseq IDs in the abundance table (data_full) are represented in the mapper files. And if not, find the lineage information and manually add it to the mapper file.

```{r}
setdiff(data_full$X, row.names(mapper)) 
# Everything is represented in the mapper! Yay! 
```

```{r}
# OG code
sample_names <- colnames(data_full)

data_species <- data_full %>% 
  mutate(X = mapper[X, "Full_name"]) %>% 
  group_by(X) %>% 
  summarise(across(where(is.numeric), sum)) %>% 
  ungroup() %>%
  select(all_of(sample_names)) %>% 
  as.data.frame()

rm(sample_names)

```

```{r}
# # Run rarefaction
# sample_names <- colnames(data_full)
# 
# data_species_rare <- data_full %>% 
#   mutate(X = mapper[X, "TaxID"]) %>% 
#   group_by(X) %>% 
#   summarise(across(where(is.numeric), sum)) %>% 
#   ungroup() %>%
#   select(sample_names) %>% 
#   select(-APHD00489) %>% # remove the adelgid
#   mutate(across(where(is.numeric), ~as.integer(.x))) %>% # Make all counts integers
#   column_to_rownames(var = "X") %>% 
#   as.data.frame()
# 
# rm(sample_names)
# 
# # Find the minimum library size (the sample with the fewest reads)
# raremax <- min(rowSums(data_species_rare))
# # Rarify the data (this takes a minute)
# set.seed(1025)
# data_species_rare <- rrarefy(data_species_rare,raremax) %>% 
#   as.data.frame()
# 
# # Pathogen richness
# data_pathogens_rare <- data_species_rare %>% 
#   filter(rownames(.) %in% pathogen_reference$taxid)
# 
# holdMe <- data_pathogens_rare
#   # t() %>% 
#   # as.data.frame() %>% 
#   # mutate(
#   #   across(where(is.numeric),
#   #          ~ if_else(.x < 25, 0, .x)) # set values below "thresh" to 0 
#   # ) %>% 
#   # t() %>% 
#   # as.data.frame()
# 
# # Separate out the fungi and bacteria
# holdMe_bac <- holdMe %>%
#   filter(rownames(.) %in% mapper$TaxID[mapper$Domain == "Bacteria"])
# 
# holdMe_fun <- holdMe %>%
#   filter(rownames(.) %in% mapper$TaxID[mapper$Kingdom == "Fungi"])
# 
# # Same order  
# identical(rownames(holdMe_bac), metadata$Number)
# identical(rownames(holdMe_fun), metadata$Number)
# 
# # Make a richness column
# # metadata$richness <- specnumber(holdMe)
# # metadata$richness_bac <- specnumber(holdMe_bac)
# # metadata$richness_fun <- specnumber(holdMe_fun)
# # meta_graph <- metadata %>% 
# #   filter(Family != "Adelgidae")
# 
#   # data_pathogens_rare <- data_species_rare %>% 
#   # t() %>% 
#   # as.data.frame() %>% 
#   # filter(rownames(.) %in% pathogen_reference$taxid) %>%
#   # filter(rownames(.) %in% mapper$TaxID[mapper$Domain == "Bacteria"])

```

## Filter abundance data (6 RPM)

```{r}
# Calculate the raw read count needed to get to 3 RPM for each sample
raw_total <- data_species %>% 
  select(-X) %>% 
  colSums() 
raw_thresh <- ceiling(raw_total * 0.000006) # Filter by 6 RPM
# New data_frame
holdMe <- as.data.frame(data_species$X)
count = 2
holdCol <- colnames(data_species)
# Iterate over each sample and set reads below the sample threshold to 0
for (i in raw_thresh) {
  new_row <- data_species[[holdCol[count]]] %>% 
    ifelse(. >= i, ., 0)
  holdMe <- cbind(holdMe, new_row)
  count = count + 1
}
colnames(holdMe) <- holdCol
# Remove microbes which have no reads in any sample
holdMe <-  holdMe %>%
  filter(rowSums(across(-X)) > 0)
# How many reads did I remove from each sample? 
(data_species %>% select(-X) %>% 
  summarise(across(everything(), ~ sum(., na.rm = TRUE)))) - (holdMe %>% 
  select(-X) %>% 
  summarise(across(everything(), ~ sum(., na.rm = TRUE))))

data_species <- holdMe
```

```{r}
# Get the pathogen list
pathogen_reference <- read.delim(file = "../../Data/Pathogen_reference_list.tsv", 
                                 header = TRUE, 
                                 sep = "\t")

# Move this later 
# Check for pathogens
# Isolate the taxID from the pathogen reference list
path_ref_taxids <- pathogen_reference %>%
  pull(taxid) %>% 
  unique(.)

# Pull all the rows from mapper that match with the given pathogen reference taxIDs
matched_mapper_rows <- mapper %>%
  filter(TaxID %in% path_ref_taxids) %>%
  pull(Full_name)

# Pull all the rows from the data frame that match with matched_mapper_rows
data_pathogens <- data_species %>% 
  filter(X %in% matched_mapper_rows) %>% 
  # mutate(across(where(is.numeric), ~ifelse((.x > 25), .x, 0))) %>% 
  filter(rowSums(across(where(is.numeric))) > 0)
```

## % of detected raw read counts match to pathogens and non-pathogens

```{r}
# Pathogens
Per_path <- (data_pathogens %>% select(-X) %>% 
  summarise(across(everything(), ~ sum(., na.rm = TRUE)))) / (data_species %>% select(-X) %>% 
  summarise(across(everything(), ~ sum(., na.rm = TRUE))))
Per_path <- Per_path %>% 
  t() %>% 
  as.data.frame() %>% 
  pull("V1")
mean(Per_path)

min(Per_path)
max(Per_path)

# Non-pathogens
mean(1 - Per_path)
```

## Filter the abundance data (drop last 5% of taxa from each sample)

```{r}
# Make the final data frame
data_clean <- data_species

for (i in 2:ncol(data_clean)) {
  # Get sample name
  sample = colnames(data_clean)[i]
  # grab the taxa to be discarded 
  # Order the data frame by one of the samples (this does not change row #s)
  taxa_cut <- data_clean %>% 
    arrange(-desc(.data[[sample]])) %>% # arrange taxa smallest to largest read count by sample
    filter(.data[[sample]] > 0)  %>% # Remove taxa where the sample has 0 reads
    slice_head(prop = 0.05) %>% # grab the 5% of taxa with the lowest read count
    pull(X) # Pull out the names of the taxa we are going to set to 0 reads for this sample
  
  # Set the cut taxa values to 0 for the given sample
  data_clean[data_clean$X %in% taxa_cut, sample] <- 0
}

# Remove any rows where the total reads in that row is also 0
data_clean <- data_clean %>%
  filter(rowSums(across(-X)) > 0)

# Check that the for loop didn't destroy the data
holdMe <- data_species %>% 
  select(-X) %>% 
  summarise(across(everything(), ~ sum(., na.rm = TRUE))) %>% 
  t() %>% 
  as.data.frame() %>% 
  pull(V1)

data_species %>% 
  select(-X) %>% 
  summarise(across(everything(), ~ sum(., na.rm = TRUE)))

data_clean %>% 
  select(-X) %>% 
  summarise(across(everything(), ~ sum(., na.rm = TRUE)))

# Make clean the new table moving forward
data_species <- data_clean
rm(data_clean)
```

## Filter the abundance data (drop species whose relative abundance \< 0.005%)

```{r}
# Make the final data frame
data_clean <- data_species

# Get the total number of reads in each sample
data_sum <- data_species %>% 
  select(-X) %>% 
  summarise(across(everything(), ~ sum(., na.rm = TRUE)))
for (i in 2:ncol(data_clean)) {
  # Get sample name
  sample = colnames(data_clean)[i]
  # Calculate the read count threshold required for meeting 0.005% relAbun
  # Get the total number of reads
  Tc <- data_sum[1,sample]
  # Calculate the read count threshold needed to be at 0.005% relAbund
  threshold <- (Tc*0.00005)
  # Set counts that do not meet the threshold to 0
  data_clean[[sample]] <- ifelse(data_clean[[sample]] < threshold,
                                      0,
                                      data_clean[[sample]])
}
# Remove any rows where the total reads in that row is also 0
data_clean <- data_clean %>%
  filter(rowSums(across(-X)) > 0)


# Are any pathogens left?
pathos <- data_clean %>% 
  filter(X %in% pathogen_reference$taxid) %>% 
  mutate(X = pathogen_reference$name[pathogen_reference$taxid == X])
```

### Histogram code if you need it

```{r}
# Just a visualization to see what the reads are that map to everything
data_look <- data_species %>%
  column_to_rownames("X") %>%
  as.data.frame() %>% 
  mutate(across(where(is.numeric), ~as.integer(.x)))
  
  # mutate(sum = rowSums(across(where(is.numeric)))

hist(data_look$APHD00095[data_look$APHD00095 > 50 & data_look$APHD00095 < 2000])
library(ggpubr)
ggdensity(data_look$APHD00095[data_look$APHD00095 > 25 & data_look$APHD00095 < 1000])

```
