---
title: "Process_abundance_table"
author: "Caitlin Loeffler"
date: "2025-06-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Boiler Plate

```{r}
library(dplyr)
library(ggplot2)
library(tibble)
library(readxl)
library(hilldiv)
library(vegan)
```
## Get the mapper files

And correct the mapper_suppressed file that got a little mixed up on the HPC.

```{r}
# Get the two mapper files
mapper_reliable <- read.delim("../../Data/Accession_taxid_lineage.tsv", 
                     header = TRUE,
                     sep = "\t", 
                     fill = TRUE) %>% 
  distinct() %>% 
  column_to_rownames(var = "Accession")


mapper_suppressed <- read.delim("../../Data/Suppressed_accession_taxid_lineage_updated.tsv", 
                                header = TRUE,
                                sep = "\t", 
                                row.names = 1) %>% # Make the Accessions the row names
  select(TaxID, Domain, Kingdom, Phylum, Class, Order, Family, Genus, Species, Full_name, Rank)

mapper <- rbind(mapper_reliable, mapper_suppressed)

# # The mapper_suppressed has some columns out of order, we are going to reorder them
# unordered_columns <- mapper_suppressed %>% 
#   filter(Full_name == "") %>% 
#   select(TaxID, Status, Comment, Domain, Kingdom, Phylum, Class, Order, Family, Genus, 
#          Species, Full_name, Rank) # Reorder the columns
# #Rename the columns
# colnames(unordered_columns) <- c("TaxID", "Domain", "Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "Species", "Full_name", "Rank", "Status", "Comment")
# # Now remake the mapper_suppressed table
# mapper_suppressed <- mapper_suppressed %>% 
#   filter(Full_name != "") %>% # Isolate the lines that are fine
#   rbind(., unordered_columns) # Bind the rows with corrected order of columns
# rm(unordered_columns)
# # Save the new table
# write.table(mapper_suppressed, file = "../../Data/Suppressed_accession_taxid_lineage_updated.tsv",
#             quote = FALSE, row.names = TRUE, sep = "\t")
```


## Get the abundance data

```{r}
# OG new data set ../../Data/Test new full alignment/CombinedTableAllSamples.txt
data_full <- read.delim( "../../Data/CombinedTableAllSamples_full.tsv", # "../../Data_clean/CombinedTableAllSamples_8_14_26.txt", # "../../Data/CombinedTableAllSamples_full.tsv"
                        header = TRUE, 
                        row.names = "X",
                        sep = "\t") %>%
  t() %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "X") %>% 
  mutate(X = sub("\\.sam\\.report$", "", X)) %>% # remove ".sam.report"
  mutate(X = sub("_S\\d+", "", X)) %>% 
  column_to_rownames(var = "X") %>% 
  t() %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "X") %>% 
  as.data.frame() 

# OG code -- Translate the RefSeqIDs to species names
sample_names <- colnames(data_full)

data_taxid <- data_full %>% 
  mutate(X = mapper[X, "TaxID"]) %>% 
  group_by(X) %>% 
  summarise(across(where(is.numeric), sum)) %>% 
  ungroup() %>%
  select(all_of(sample_names)) %>% 
  as.data.frame()

rm(sample_names)


# Check that all the refSeqIDs in the data are also represented in the mapper
setdiff(data_full$X, row.names(mapper))
```


## Filter abundance data (6 RPM) --- TAXIDS

```{r}
# Calculate the raw read count needed to get to 6 RPM for each sample
raw_total <- data_taxid %>% 
  select(-X) %>% 
  colSums() 
raw_thresh <- ceiling(raw_total * 0.000006) # Filter by 6 RPM
# New data_frame
holdMe <- as.data.frame(data_taxid$X)
count = 2
holdCol <- colnames(data_taxid)
# Iterate over each sample and set reads below the sample threshold to 0
for (i in raw_thresh) {
  new_row <- data_taxid[[holdCol[count]]] %>% 
    ifelse(. >= i, ., 0)
  holdMe <- cbind(holdMe, new_row)
  count = count + 1
}
colnames(holdMe) <- holdCol
# Remove microbes which have no reads in any sample
holdMe <-  holdMe %>%
  filter(rowSums(across(-X)) > 0)
# How many reads did I remove from each sample? 
(data_taxid %>% select(-X) %>% 
  summarise(across(everything(), ~ sum(., na.rm = TRUE)))) - (holdMe %>% 
  select(-X) %>% 
  summarise(across(everything(), ~ sum(., na.rm = TRUE))))

data_taxid <- holdMe
```
# Identify pathogens

```{r}
# Load the pathogen reference list
pathogen_reference <- read.delim(file = "../../Data/Pathogen_reference_list.tsv", 
                                 header = TRUE, 
                                 sep = "\t")

# Isolate the taxID from the pathogen reference list
path_ref_taxids <- pathogen_reference %>%
  pull(taxid) %>% 
  unique(.)

# Pull all the rows from the data frame that match with matched_mapper_rows
data_pathogens <- data_taxid %>% 
  filter(X %in% path_ref_taxids)
```



# Other stuff ------------------------------------------------------------------
## Grab the metadata table

```{r}
metadata <- read_excel(path = "../../Data/Owen_insect_tissues_WorkSheet.xlsx", 
                       sheet = "GWU_RNAseq_2024") %>%
  filter(!if_all(everything(), is.na)) %>% 
  select(Number, Family, `Collection Date`) 
```

Check that all the refseq IDs in the abundance table (data_full) are represented in the mapper files. And if not, find the lineage information and manually add it to the mapper file.

```{r}
setdiff(data_full$X, row.names(mapper)) 



# setdiff(data_full$X, row.names(mapper)) %>% 
#   write.table("../../Data/Test new full alignment/New_refseqIDs.tsv", sep = "\t", row.names = FALSE, quote = FALSE, col.names = FALSE)

```

```{r}
sample_names <- colnames(data_full)

data_species <- data_full %>% 
  mutate(X = mapper[X, "Full_name"]) %>% 
  group_by(X) %>% 
  summarise(across(where(is.numeric), sum)) %>% 
  ungroup() %>%
  select(all_of(sample_names)) %>% 
  as.data.frame()

rm(sample_names)

```


## Filter abundance data (6 RPM)--- FULL NAME

```{r}
# Calculate the raw read count needed to get to 6 RPM for each sample
raw_total <- data_species %>% 
  select(-X) %>% 
  colSums() 
raw_thresh <- ceiling(raw_total * 0.000006) # Filter by 6 RPM
# New data_frame
holdMe <- as.data.frame(data_species$X)
count = 2
holdCol <- colnames(data_species)
# Iterate over each sample and set reads below the sample threshold to 0
for (i in raw_thresh) {
  new_row <- data_species[[holdCol[count]]] %>% 
    ifelse(. >= i, ., 0)
  holdMe <- cbind(holdMe, new_row)
  count = count + 1
}
colnames(holdMe) <- holdCol
# Remove microbes which have no reads in any sample
holdMe <-  holdMe %>%
  filter(rowSums(across(-X)) > 0)
# How many reads did I remove from each sample? 
(data_species %>% select(-X) %>% 
  summarise(across(everything(), ~ sum(., na.rm = TRUE)))) - (holdMe %>% 
  select(-X) %>% 
  summarise(across(everything(), ~ sum(., na.rm = TRUE))))

data_species <- holdMe
```



# For alternative alignment

```{r}
holdMe <- mapper %>%
  select(TaxID) %>% 
  rownames_to_column(var = "X") %>%
  as.data.frame()

bindMe <- read.table("../refseq_taxids_new_8_17_26.txt", 
                     sep = "\t")
colnames(bindMe) <- c("X", "TaxID")

RefSeq_taxID_mapper <- rbind(bindMe,holdMe) %>% 
  column_to_rownames(var = "X")

# Check that nothing else is missing
setdiff(data_full$X, RefSeq_taxID_mapper$X)

# Pathogens---------------------------------------------------------------------

# Isolate the taxID from the pathogen reference list
path_ref_taxids <- pathogen_reference %>%
  pull(taxid) %>% 
  unique(.)

# Pull all the rows from mapper that match with the given pathogen reference taxIDs
matched_mapper_rows <- RefSeq_taxID_mapper %>%
  filter(TaxID %in% path_ref_taxids) %>%
  pull(X)

# Pull all the rows from the data frame that match with matched_mapper_rows
data_pathogens <- data_full %>% 
  filter(X %in% matched_mapper_rows)


```



