# Boiler Plate

```{r}
library(ggplot2)
library(dplyr)
library(reshape2)
library(patchwork)
```

# Functions

```{r}
# Isolate the data and make the bar plot
select_and_plot <- function(data, selection, legend_name, 
                            plot_title, ncol_leg = NULL, width = 1, 
                            y_lab = "", x_lab = "", swap = FALSE, x_label_tilt = 0) {
  # Make the selection
  data_graph <- data %>% 
    filter(lineage %in% selection)
  
  # Make the box plot go horizontal
  if (swap) {
    # Swap the names of value and variable column so bar plot axis swap around
    colnames(data_graph) <- c("lineage","value","variable")
  }
  
  # Make the graph
  # Create barplot of pathogens (Aphids)
  the_plot <- ggplot(data_graph, aes(fill = lineage, 
                                     y =  value, 
                                     x = variable)) + 
    geom_bar(position="stack", 
             stat="identity", 
             color = "black", 
             width = width) + 
    xlab(x_lab) + 
    ylab(y_lab) + 
    ggtitle(plot_title) + 
    guides(fill=guide_legend(title=legend_name, ncol = ncol_leg)) +
    theme(
      title = element_text(size = 18),
      axis.title = element_text(size = 16), 
      axis.text = element_text(size = 15), 
      legend.title = element_text(size = 15), 
      legend.text = element_text(size = 15), 
      axis.text.x = element_text(angle = x_label_tilt)
    )
  
  return(the_plot)
}

# Just plot
just_plot <- function(data, legend_name, 
                            plot_title, ncol_leg = NULL) {
  # Make the graph
  # Create barplot of pathogens (Aphids)
  the_plot <- ggplot(data, aes(fill = lineage, 
                                     y =  value, 
                                     x = variable)) + 
    geom_bar(position="stack", 
             stat="identity", 
             color = "black") + 
    xlab("Sample Name") + 
    ylab("Read Count") + 
    ggtitle(plot_title) + 
    guides(fill=guide_legend(title=legend_name, ncol = ncol_leg)) +
    theme(
      title = element_text(size = 18),
      axis.title = element_text(size = 16), 
      axis.text = element_text(size = 14), 
      legend.title = element_text(size = 15), 
      legend.text = element_text(size = 13),
      axis.text.x = element_text(angle = x_label_tilt)
    )
  
  return(the_plot)
}


# Get with the threshold
threshold_getter <- function(data, selection, threshold = 100) {
  # Check threshold
  data_thresh <- data %>% 
    filter(lineage %in% selection) %>% 
    mutate(value = ifelse(value < threshold, 0, value)) %>% 
    filter(value > 0) %>% 
    select(lineage, variable) %>%
    as.data.frame() %>%
    with(.,  .[order(lineage) , ]) 
  
  print(data_thresh, width = Inf)
  
}
```

# Get the metadata

```{r}
metadata <- read_excel(path = "../../Data/Owen_insect_tissues_WorkSheet.xlsx", 
                       sheet = "GWU_RNAseq_2024") %>%
  filter(!if_all(everything(), is.na)) %>% 
  select(Number, Family, `Collection Date`) 
```

# Make alignment % plots

```{r}
sample_order <- c("APHD00489","APHD00085","APHD00095","APHD00098","APHD00110","APHD00328","APHD00334","APHD00340","APHD00350","APHD00352","APHD00356","APHD00361","APHD00437","APHD00445","APHD00454","APHD00455","APHD00457","APHD00471","APHD00476","APHD00479","APHD00482","APHD00501","APHD00508","APHD00519","APHD00562","APHD00566","APHD00568","APHD00570","APHD00574","APHD00576","APHD00578","APHD00579","APHD00612","APHD00447","APHD00469","APHD00472","APHD00480","APHD00503","APHD00509","APHD00521") 

data_align <- read_excel(path = "../../Data/Owen_insect_tissues_WorkSheet.xlsx",
                         sheet = "Sheet1") %>% 
  select(Sample, Prop_aligned, unclassified) %>% 
  mutate(
    Prop_aligned = as.numeric(Prop_aligned),
    unclassified = as.numeric(unclassified) 
  ) %>% 
  rename(Aligned = Prop_aligned, 
         Unclassified = unclassified)

# Get the alignment percentages
min(data_align$Aligned)
max(data_align$Aligned)
mean(data_align$Aligned)

# reshape the bar plot
data_long <- data_align
data_long <- melt(data_long, id.vars = "Sample") %>% 
  mutate(variable = factor(variable, levels = c("Unclassified", "Aligned")),
         Sample = factor(Sample, levels = c(sample_order)))
```

Make the plots

```{r}
ggplot(data_long, aes(fill = variable, 
                      y =  value, 
                      x = Sample)) + 
  geom_bar(position="stack", 
           stat="identity", 
           color = "black") + 
  theme(axis.text.x = element_text(angle = 90)) + 
  xlab("Samples") + 
  ylab("Proportion of sample") + 
  guides(fill=guide_legend(title="Read fate")) + 
  scale_fill_manual(values = c("gray", "salmon")) + 
  labs(title = "Read Alignment %")

ggsave(file = "../../Images/Percent_Align.svg")
ggsave(file = "../../Images/Percent_Align.png")

```

# Separate ants and aphids

```{r}
# Set up the graphing data frame. 
data_long <- data_pathogens_species
data_long$lineage <- as.factor(data_long$X)
data_long <- melt(data_long[,2:ncol(data_long)], id.vars = "lineage")
data_graph <- data_long 
rm(data_long)

# What samples are ants and aphids
aphids <- metadata %>% 
  filter(Family == "Aphididae") %>% # Dropped Adelgid
  pull(Number)
ants <- metadata %>% 
  filter(Family == "Formicidae" & Number != "APHD00521") %>% 
  pull(Number)
adelgid <- metadata %>% 
  filter(Family == "Adelgidae") %>% # Dropped Adelgid
  pull(Number)

# Isolate aphids
data_graph_aphids <- data_graph %>%
  filter(variable %in% aphids) %>% 
  filter(value > 0)

# Isolate ants
data_graph_ants <- data_graph %>%
  filter(variable %in% ants) %>% 
  filter(value > 0)

# That one ant
data_graph_521 <- data_graph %>% 
  filter(variable == "APHD00521") %>% 
  filter(value > 0)

# The 1 Adelgid
data_graph_adelgid <- data_graph %>% 
  filter(variable == "APHD00489") %>% 
  filter(value > 0)
```

# Make the 3 Domain level plots

I am going to make 4 separate plots, 1 for each of Viruses, Bacteria, Fungus, and Plants (and Archaea).

Sort the identified pathogen names into the different bins.

```{r}
# Set up bin variables
Fungi <- c()
Bacteria <- c()
Viruses <- c()
Plants <- c()
Archaea <- c()
what <- c()

for (i in data_pathogens_species$X) {
  # Convert Full_name to Domain name
  domain = mapper$Domain[mapper[["Full_name"]] == i][1]
  # Use the Domian name to sort into 4 bins
  if (domain == "Eukaryota") {
    # Move down to the kingdom level
    kingdom = mapper$Kingdom[mapper[["Full_name"]] == i][1]
    # Sort into Plant and Fungus
    if (kingdom == "Fungi") {
      Fungi <- c(Fungi, i)
      next # move to the next iteration if the for loop
    } # Else it is a plant OR ALGEA
    Plants <- c(Plants, i)
    next # Move to the next iteration of the for loop
  }
  if (domain == "Bacteria") {
    Bacteria <- c(Bacteria, i)
    next # move to the next iteration of the for loop
  }
  if (domain == "Viruses") {
    Viruses <- c(Viruses, i)
    next # move to the next iteration of the for loop
  }
  if (domain == "Archaea") {
    Archaea <- c(Archaea, i)
    next # Move to the next iteration of the for loop
  } # Grab everything else (DEBUG CODE)
  what <- c(what, i) # Is empty
}

```

Sort the graphs (Bacteria, Viruses, and Fungi are the only pathogens), so there will be 3 graphs for each group

Thin out the pathogens with a threshold value first

```{r}
thresh = 0
```

```{r}
# Aphids
data_thin_aphids <- data_graph_aphids %>% 
  filter(value > thresh)
# Viruses
p1 <- select_and_plot(data = data_thin_aphids, selection = Viruses, 
                plot_title = "", legend_name = "Viruses Detected", y_lab = "", swap = TRUE) + 
  xlab("Read Count")
p1
#threshold_getter(data_thin_aphids, selection = Viruses)
# Bacteria 
p2 <- select_and_plot(data = data_thin_aphids, selection = Bacteria, 
                legend_name = "Bacteria Detected", plot_title = "", 
                ncol_leg = 1, swap = TRUE) + 
  xlab("Read Count")
p2
#threshold_getter(data_thin_aphids, selection = Bacteria, threshold = 250)
# Fungi
p3 <- select_and_plot(data = data_thin_aphids, selection = Fungi, 
                legend_name = "Fungi Detected", plot_title = "", 
                ncol_leg = 1, swap = TRUE) + 
  xlab("Read Count")
p3
#threshold_getter(data_thin_aphids, selection = Fungi, threshold = 2500)


# Combined plot
#p3/(p1|p2) 

p3 + (p1/p2) + plot_annotation(tag_levels = "a",  
                             title = "") & 
  theme(plot.tag = element_text(size = 25, face = "bold"),
        plot.tag.position = c(0.02, 1.02)) 

# ggsave(filename = "../../Images/Aphid_pathogens.svg",
#        height = 901.534,
#        width = 1725.45,
#        units = "px",
#        dpi = "screen")
# 
# ggsave(filename = "../../Images/Aphid_pathogens.png",
#        height = 700, # 700
#        width = 1339.733, # 1339.733
#        units = "px",
#        dpi = "screen")
# 
# ggsave(filename = "../../Images/Aphid_pathogens.pdf",
#        height = 901.534,
#        width = 1725.45,
#        units = "px",
#        dpi = "screen")
```

ants

```{r}
# Isolate the data and make the bar plot
select_and_plot <- function(data, selection, legend_name, 
                            plot_title, ncol_leg = NULL, width = 1, 
                            y_lab = "Read Count") {
  # Make the selection
  data_graph <- data %>% 
    filter(lineage %in% selection)
  
  # Make the graph
  # Create barplot of pathogens (Aphids)
  the_plot <- ggplot(data_graph, aes(fill = lineage, 
                                     y =  value, 
                                     x = variable)) + 
    geom_bar(position="stack", 
             stat="identity", 
             color = "black", 
             width = width) + 
    theme(axis.text.x = element_text(angle = 90)) + 
    xlab("") + 
    ylab(y_lab) + 
    ggtitle(plot_title) + 
    guides(fill=guide_legend(title=legend_name, ncol = ncol_leg)) +
    theme(
      title = element_text(size = 18),
      axis.title = element_text(size = 16), 
      axis.text = element_text(size = 15), 
      legend.title = element_text(size = 15), 
      legend.text = element_text(size = 15)
    )
  
  return(the_plot)
}
```

```{r}
# Ants
data_thin_ants <- data_graph_ants %>% 
  filter(value > thresh) 

# Viruses
p1 <- select_and_plot(data = data_thin_ants, selection = Viruses, 
                plot_title = "", legend_name = "Viruses Detected") + 
  ylab("Read Count")
p1
#threshold_getter(data_thin_ants, selection = Viruses)
# Bacteria 
p2 <- select_and_plot(data = data_thin_ants, selection = Bacteria, 
                legend_name = "Bacteria Detected", plot_title = "", 
                ncol_leg = 1, x_label_tilt = 90) + 
  ylab("Read Count")
p2
#threshold_getter(data_thin_ants, selection = Bacteria, threshold = 250)
# Fungi
p3 <- select_and_plot(data = data_thin_ants, selection = Fungi, 
                legend_name = "Fungi Detected", plot_title = "", 
                ncol_leg = 1, x_label_tilt = 90) + 
  ylab("Read Count") 
p3
#threshold_getter(data_thin_ants, selection = Fungi, threshold = 2500)
```

The last ant

```{r}
library(scales)
show_col(hue_pal()(7))
```

```{r}
# That last ant 
data_thin_521 <- data_graph_521 %>% 
  filter(value > thresh) 

# Viruses
p4 <- select_and_plot(data = data_thin_521, selection = Viruses, 
                plot_title = "", legend_name = "Viruses Detected") +
  ylab("Read Count") + theme(axis.text.x = element_blank())
p4
#threshold_getter(data_thin_521, selection = Viruses)
# Bacteria 
p5 <- select_and_plot(data = data_thin_521, selection = Bacteria, 
                legend_name = "Bacteria Detected", plot_title = "",
                ncol_leg = 1, width = 0.25) +
  ylab("Read Count") + theme(axis.text.x = element_blank())
p5
#threshold_getter(data_thin_521, selection = Bacteria, threshold = 250)

# Bacteria, now without Pantoea agglomerans, so I can see the other read counts
data_thin_521 <- data_graph_521 %>% 
  filter(value > thresh) %>% 
  filter(lineage != "Pantoea agglomerans")
p6 <- select_and_plot(data = data_thin_521, selection = Bacteria, 
                legend_name = "Bacteria Detected", plot_title = "",
                ncol_leg = 1, width = 0.5) +
  ylab("Read Count") + 
  scale_fill_manual(values = c("#C49A00","#53B400","#00C094","#00B6EB","#A58AFF","#FB61D7"
)) + theme(axis.text.x = element_blank())
p6
# Fungi
p7 <- select_and_plot(data = data_thin_521, selection = Fungi, 
                legend_name = "Fungi Detected", plot_title = "", 
                ncol_leg = 1, width = 0.10) +
  ylab("Read Count") + theme(axis.text.x = element_blank())
p7
#threshold_getter(data_thin_521, selection = Fungi, threshold = 2500)
```

Ant combined plot

```{r}
(p3 | p2)/ (p5 | p6 | p7) + plot_annotation(tag_levels = "a", 
                             title = "") & 
  theme(plot.tag = element_text(size = 25, face = "bold"),
        plot.tag.position = c(0.02, 1.02)) 


ggsave(filename = "../../Images/Ant_pathogens.svg",
       height = 900,
       width = 1339.733,
       units = "px",
       dpi = "screen")

ggsave(filename = "../../Images/Ant_pathogens.png",
       height = 900, # 700
       width = 1339.733,
       units = "px",
       dpi = "screen")


```

Adelgid

```{r}
# Adelgid
data_thin_adelgid <- data_graph_adelgid %>% 
  filter(value > thresh)
# Viruses
select_and_plot(data = data_thin_adelgid, selection = Viruses, 
                plot_title = "Adelgid sample", legend_name = "Viruses Detected")
threshold_getter(data_thin_adelgid, selection = Viruses)

# Bacteria 
select_and_plot(data = data_thin_adelgid, selection = Bacteria, 
                legend_name = "Bacteria Detected", plot_title = "Adelgid sample",
                ncol_leg = 1)
threshold_getter(data_thin_adelgid, selection = Bacteria, threshold = 250)
# Fungi
select_and_plot(data = data_thin_adelgid, selection = Fungi, 
                legend_name = "Fungi Detected", plot_title = "Adelgid sample", 
                ncol_leg = 1) + 
  ylab("Read Count")
threshold_getter(data_thin_adelgid, selection = Fungi, threshold = 2500)

# Save the plot
ggsave(filename = "../../Images/Adelgid_pathogens.svg",
       height = 350,
       width = 300,
       units = "px",
       dpi = "screen")

ggsave(filename = "../../Images/Adelgid_pathogens.png",
       height = 350, # 700
       width = 300,
       units = "px",
       dpi = "screen")

```

.

.

.

.

.

.

.

.

.

.

# Now lets make the general ones for Plants

### Function

```{r}
# 
grab_and_group <- function(data, map, map_sup, level = "Species") {
  # Set the X (nucleotide refID) of the new data frame to the pathogen name
  for (i in 1:nrow(data)) {
    # Isolate the RefSeqID
    RefSeqID <- data[i,"X"] %>%
      as.character(.)
    
    # Lets make a try catch for tha mapper files instead of an if statement
    if (RefSeqID %in% rownames(map)) {
      #Pull the full name from the mapper file
      name <- map[[RefSeqID , level]]
      #Replace the RefSeqID with the full name
      data[i, "X"] = name
      next
    }else{
      #Pull the full name from the mapper file
      name <- map_sup[[RefSeqID , level]]
      #Replace the RefSeqID with the full name
      data[i, "X"] = name
    }
    
  }
  
  # Now we need to combine rows where taxa are the same
  data_new <- data %>% 
    group_by(X) %>% 
    summarise(across(where(is.numeric), sum)) %>% 
    ungroup()
  
  return(data_new)
}

```

Plants

```{r}
# Isolate rows that are all plants in abundance data
# Idenfity which refIDs are Viridiplantae (which I already have a funciton for!)
data_plants <- data_full %>%
  infection_isolator(., level = "Kingdom", taxa = "Viridiplantae", 
                     map = mapper, map_sup = mapper_suppressed) %>% 
  grab_and_group(., mapper, map_sup = mapper_suppressed, level = "Genus") # Convert refIds to names, sum where they are the same

# Set up the graphing data frame. 
data_long <- data_plants
data_long$lineage <- as.factor(data_long$X)
data_long <- melt(data_long[,2:ncol(data_long)], id.vars = "lineage")
data_graph_plants <- data_long %>% 
  mutate(variable = sub("\\.sam\\.report$", "", variable)) %>% # remove ".sam.report"
  mutate(variable = sub("_S\\d+", "", variable))
rm(data_long)

# Sort into Sample Taxa
# Isolate aphids
data_graph_plants_aphids <- data_graph_plants %>%
  filter(variable %in% aphids) %>% 
  filter(value > 0)

# Isolate ants
data_graph_plants_ants <- data_graph_plants %>%
  filter(variable %in% ants) %>% 
  filter(value > 0)

# That one ant
data_graph_plants_521 <- data_graph_plants %>% 
  filter(variable == "APHD00521") %>% 
  filter(value > 0)

# Make the plots
just_plot(data_graph_plants_aphids, legend_name = "Plant Genera", plot_title = "Aphid Samples", ncol_leg = 4)

just_plot(data_graph_plants_ants, legend_name = "Plant Genera", plot_title = "Ant Samples", ncol_leg = 4)

just_plot(data_graph_plants_521, legend_name = "Plant Genera", plot_title = "Ant sample 521", ncol_leg = 2)
```

Bacteria

```{r}
# Isolate rows that are all plants in abundance data
# Idenfity which refIDs are Viridiplantae (which I already have a funciton for!)
data_bacteria <- data_full %>%
  infection_isolator(., level = "Domain", taxa = "Bacteria", 
                     map = mapper, map_sup = mapper_suppressed) %>% 
  grab_and_group(., mapper, map_sup = mapper_suppressed, level = "Phylum") # Convert refIds to names, sum where they are the same

# Set up the graphing data frame. 
data_long <- data_bacteria
data_long$lineage <- as.factor(data_long$X)
data_long <- melt(data_long[,2:ncol(data_long)], id.vars = "lineage")
data_graph_bacteria <- data_long %>% 
  mutate(variable = sub("\\.sam\\.report$", "", variable)) %>% # remove ".sam.report"
  mutate(variable = sub("_S\\d+", "", variable))
rm(data_long)

# Sort into Sample Taxa
# Isolate aphids
data_graph_bacteria_aphids <- data_graph_bacteria %>%
  filter(variable %in% aphids) %>% 
  filter(value > 0)

# Isolate ants
data_graph_bacteria_ants <- data_graph_bacteria %>%
  filter(variable %in% ants) %>% 
  filter(value > 0)

# That one ant
data_graph_bacteria_521 <- data_graph_bacteria %>% 
  filter(variable == "APHD00521") %>% 
  filter(value > 0)

# Make the plots
just_plot(data_graph_bacteria_aphids, legend_name = "Bacterial Phyla", plot_title = "Aphid Samples", ncol_leg = 1)

just_plot(data_graph_bacteria_ants, legend_name = "Bacterial Phyla", plot_title = "Ants Samples", ncol_leg = 1)

just_plot(data_graph_bacteria_521, legend_name = "Bacterial Phyla", plot_title = "Ant Sample 521", ncol_leg = 1)
```

Viruses

```{r}
# Isolate rows that are all plants in abundance data
# Idenfity which refIDs are Viridiplantae (which I already have a funciton for!)
data_virus <- data_full %>%
  infection_isolator(., level = "Domain", taxa = "Viruses", 
                     map = mapper, map_sup = mapper_suppressed) %>% 
  grab_and_group(., mapper, map_sup = mapper_suppressed, level = "Species") # Convert refIds to names, sum where they are the same

# Set up the graphing data frame. 
data_long <- data_virus
data_long$lineage <- as.factor(data_long$X)
data_long <- melt(data_long[,2:ncol(data_long)], id.vars = "lineage")
data_graph_virus <- data_long %>% 
  mutate(variable = sub("\\.sam\\.report$", "", variable)) %>% # remove ".sam.report"
  mutate(variable = sub("_S\\d+", "", variable))
rm(data_long)

# Sort into Sample Taxa
# Isolate aphids
data_graph_virus_aphids <- data_graph_virus %>%
  filter(variable %in% aphids) %>% 
  filter(value > 0)

# Isolate ants
data_graph_virus_ants <- data_graph_virus %>%
  filter(variable %in% ants) %>% 
  filter(value > 0)

# That one ant
data_graph_virus_521 <- data_graph_virus %>% 
  filter(variable == "APHD00521") %>% 
  filter(value > 0)

# Make the plots
just_plot(data_graph_virus_aphids, legend_name = "Viruses", plot_title = "Aphid Samples", ncol_leg = 2)

just_plot(data_graph_virus_ants, legend_name = "Viruses", plot_title = "Ants Samples", ncol_leg = 2)

just_plot(data_graph_virus_521, legend_name = "Viruses", plot_title = "Ant Sample 521", ncol_leg = 1)
```

Fungi

```{r}
# Isolate rows that are all plants in abundance data
# Idenfity which refIDs are Viridiplantae (which I already have a funciton for!)
data_fungi <- data_full %>%
  infection_isolator(., level = "Kingdom", taxa = "Fungi", 
                     map = mapper, map_sup = mapper_suppressed) %>% 
  grab_and_group(., mapper, map_sup = mapper_suppressed, level = "Phylum") # Convert refIds to names, sum where they are the same

# Set up the graphing data frame. 
data_long <- data_fungi
data_long$lineage <- as.factor(data_long$X)
data_long <- melt(data_long[,2:ncol(data_long)], id.vars = "lineage")
data_graph_fungi <- data_long %>% 
  mutate(variable = sub("\\.sam\\.report$", "", variable)) %>% # remove ".sam.report"
  mutate(variable = sub("_S\\d+", "", variable))
rm(data_long)

# Sort into Sample Taxa
# Isolate aphids
data_graph_fungi_aphids <- data_graph_fungi %>%
  filter(variable %in% aphids) %>% 
  filter(value > 0)

# Isolate ants
data_graph_fungi_ants <- data_graph_fungi %>%
  filter(variable %in% ants) %>% 
  filter(value > 0)

# That one ant
data_graph_fungi_521 <- data_graph_fungi %>% 
  filter(variable == "APHD00521") %>% 
  filter(value > 0)

# Make the plots
just_plot(data_graph_fungi_aphids, legend_name = "Fungal Phyla", plot_title = "Aphid Samples", ncol_leg = 1)

just_plot(data_graph_fungi_ants, legend_name = "Fungal Phyla", plot_title = "Ant Samples", ncol_leg = 1)

just_plot(data_graph_fungi_521, legend_name = "Fungal Phyla", plot_title = "Ant Sample 521", ncol_leg = 1)
```

Archaea

```{r}
# Isolate rows that are all plants in abundance data
# Idenfity which refIDs are Viridiplantae (which I already have a funciton for!)
data_fungi <- data_full %>%
  infection_isolator(., level = "Domain", taxa = "Archaea", 
                     map = mapper, map_sup = mapper_suppressed) %>% 
  grab_and_group(., mapper, map_sup = mapper_suppressed, level = "Phylum") # Convert refIds to names, sum where they are the same

# Set up the graphing data frame. 
data_long <- data_fungi
data_long$lineage <- as.factor(data_long$X)
data_long <- melt(data_long[,2:ncol(data_long)], id.vars = "lineage")
data_graph_fungi <- data_long %>% 
  mutate(variable = sub("\\.sam\\.report$", "", variable)) %>% # remove ".sam.report"
  mutate(variable = sub("_S\\d+", "", variable))
rm(data_long)

# Sort into Sample Taxa
# Isolate aphids
data_graph_fungi_aphids <- data_graph_fungi %>%
  filter(variable %in% aphids) %>% 
  filter(value > 0)

# Isolate ants
data_graph_fungi_ants <- data_graph_fungi %>%
  filter(variable %in% ants) %>% 
  filter(value > 0)

# That one ant
data_graph_fungi_521 <- data_graph_fungi %>% 
  filter(variable == "APHD00521") %>% 
  filter(value > 0)

# Make the plots
just_plot(data_graph_fungi_aphids, legend_name = "Archaeal Phyla", plot_title = "Aphid Samples", ncol_leg = 1)

just_plot(data_graph_fungi_ants, legend_name = "Archaeal Phyla", plot_title = "Ants Samples", ncol_leg = 1)

just_plot(data_graph_fungi_521, legend_name = "Archaeal Phyla", plot_title = "Ant Sample 521", ncol_leg = 1)
```
